Enhancing Forecast Reconciliation: A Study of Alternative Covariance Estimators

### 2025-04-29 research_proposal/research_proposal.qmd
shortcoming of shrinkage and intro to NOVELIST

-   Novelist
-   POET
-   Novelist with PC-adjusted

>>>>

The optimal lambda is obtained by minimising the $MSE(\hat{\boldsymbol{W}}_1) = Bias(\hat{\boldsymbol{W}}_1)^2 + Var(\hat{\boldsymbol{W}}_1)$. More specifically, we trade the unbiasedness of the sample covariance matrix for a lower variance. The objective function itself does not take into account any possible principal components structure in the data, and is not flexible enough since it shrinks all off-diagonal elements equally towards zeros.

***NOVELIST***

The NOVELIST (NOVEL Integration of the Sample and Thresholded Covariance) estimator, proposed by Huang & Fryzlewicz (2019), is currently the main focus of this research project. It is based on the idea of soft-thresholding the sample covariance matrix, then performing shrinkage towards this thresholded version. This introduces an extra parameter, the threshold $\delta$, which is used to control the amount of soft-thresholding, offering more flexibility. The NOVELIST estimator is given by:

-   POET
-   Novelist with PC-adjusted
